Capstone Movielens Report

### 2025-10-26 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function: msg.set_arg.

Builds a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument using the format element specified by the following arguments:

  - [arg.name](#func.msg.set_arg.args.arg.name): the pattern to be replaced by the value passed in the [arg](#func.msg.set_arg.args.arg) argument;

  - [arg](#func.msg.set_arg.args.arg): the value to replace all occurrences of the pattern passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument.

@@

```{r eval=FALSE}
msg.set_arg(msg_template, arg, arg, arg.name = "%1")
```
:::

@@

::: { #func.msg.set_arg.args.arg.name .sidebar }
  - **arg.name:** Substring to replace in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.

@@

::: { #func.msg.set_arg.args.arg .sidebar }
  - **arg:** Value to replace the format elements represented by the substring specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument. 
:::
:::

>>>>

Creates a character vector from the template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument, using the value specified by the [arg](#func.msg.set_arg.args.arg) argument to replace all the occurrences of the placeholder passed in the [arg.name](#func.msg.set_arg.args.arg.name) argument found in the template.

@@

```{r eval=FALSE}
msg.set_arg(msg_template, arg, arg.name = "%1")
```
:::

@@

::: { #func.msg.set_arg.args.arg.name .sidebar }
  - **arg.name:** Substring (pattern) to replace all occurrences found in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument with the value specified in the [arg](#func.msg.set_arg.args.arg) argument.

@@

::: { #func.msg.set_arg.args.arg .sidebar }
  - **arg:** Value to replace all occurrences of the pattern specified by the [arg.name](#func.msg.set_arg.args.arg.name) argument in the message template passed in the [msg_template](#func.msg.set_arg.args.msg_template) argument.
